---
title: "Introduction to parsetR"
author: "Kenton Russell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to parsetR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Parallel Sets

Parallel sets first [published](http://kosara.net/papers/2006/Kosara_TVCG_2006.pdf) by Robert Kosara in 

<blockquote>
Kosara, Robert, Fabian Bendix, and Helwig Hauser. "Parallel sets: Interactive exploration and visual analysis of categorical data." Visualization and Computer Graphics, IEEE Transactions on 12.4 (2006): 558-568.
</blockquote>

provide a compelling interactive method for visualizing categorical data.  [Jason Davies](https://www.jasondavies.com/), co-author of [`d3.js`](https://github.com/mbostock/d3/graphs/contributors), implemented an extremely well-designed [`d3` version of parallel sets](https://www.jasondavies.com/parallel-sets/).  Using the infrastructure provided by [`htmlwidgets`](http://htmlwidgets.org), this package `parsetR` allows us to easily integrate parallel sets into our R workflow.

## Installation

`parsetR` is not on CRAN, so please install using `devtools::install_github()`.

```{r eval = FALSE}
devtools::install_github("timelyportfolio/parsetR")
```

## Usage

### With `table`

In this first iteration, `parsetR` is designed to work with `tables` from R, such as the built-in `Titanic` dataset.

```{r}
library(parsetR)

parset(Titanic, width = "80%", height = 400)
```

Here is another example with the `UCBAdmissions` data, and we'll make the lines curvy with the `tension` argument.

```{r}
library(parsetR)

parset(UCBAdmissions, tension = 0.5, width = "80%", height = 400)
```

### With `data.frame`

With a `data.frame` you'll need to tell `parsetR` where to find the numeric column for now.  Otherwise, it will appear as a dimension. as shown below.  

```{r}
# demonstrate working with non-table
data(Alligator, package="vcdExtra")
# with data.frame to demo how it doesn't work
parset(Alligator, width = "80%", height = 400)
```

I thought it be fun to force a little `JavaScript` to specify our numeric `value`.  I will eventually provide a more `R`-like interface, but for now please learn this tiny bit of JS :). 

```{r}
parset(
  Alligator,
  # dimensions are the categorical columns
  dimensions = colnames(Alligator)[-5],
  # use some JavaScript to inform parset that Freq has the value
  value = htmlwidgets::JS("function(d){return d.count}"),
  width = "80%", height = 400
)
```

## Feedback

`parsetR` was implemented in a couple of hours to provide a base for feedback, criticism, comments.  Please help me make this thing as good as it should be.
